Endogenous Politics and \\ the Design of Trade Institutions

### 2017-01-02 to-do.tex
add notes on joint surplus in my model

@@

>>>>

						\item In my model, optimum for lobby would be prohibitive tariff, $e=0$. Joint optimum determined by $\frac{\partial \ga}{\partial e}\pi_X = 2$ and $\frac{\partial CS_X}{\partial \tau} + \left[ 1 + \ga(e)\right]\frac{\partial \pi_X}{\partial \tau} + \frac{\partial TR}{\partial \tau} = 0$. Not clear how this is related to lobby's problem, but likely to have higher $\tau$ and lower $e$ than government's optimum (unless $\ga$ changes very steeply between the two points $e_J$ and $e_G$)

@@

				\item If I change nothing else but subtract $C$ from gov't welfare function, no qualitative change b/c of 0 bargaining weight
